\documentclass[jou,12pt,a4paper]{apa6}

%%%%%%%%%%%%%%%%%%%% Loading packages %%%%%%%%%%%%%%%%%%%% 
\usepackage{csquotes}
\usepackage[american]{babel}
\usepackage{amsmath, amssymb, graphicx,gensymb}
\usepackage{fixltx2e} % Misc Latex fixes
\usepackage{url}
\usepackage{threeparttable}
\usepackage[capposition=top]{floatrow}
\usepackage[colorlinks=true,citecolor=blue]{hyperref}
\usepackage{apacite}

%%%%%%%%%%%%%%%%%%%% Set some paramters %%%%%%%%%%%%%%%%%%
\setlength{\parindent}{10mm}
\setlength{\parskip}{0mm}
\graphicspath{ {Figures/} } % path to images

%%%%%%%%%%%%%%%%%%%% Title and such %%%%%%%%%%%%%%%%%%%%%%
\title{\Large Investigating the representational dimensionality and spatial distribution of functional neural networks}
\shorttitle{Dimensionality of functional neural networks}

\author{Lukas Snoek}
\affiliation{University of Amsterdam\\[\baselineskip]
\large Research Master Psychology}
\authornote{Lukas Snoek, student nr. 10126228, University of Amsterdam, Email: lukassnoek@gmail.nl.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  OPTIONAL STUFF  									
%	\leftheader{Snoek}		ONLY IN [jou] MODE			
%	\journal{Journal of Awesomeness}					
%	\volume{2(3)}										
%	\note{version 1}									
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\abstract{In the past decade, cognitive neuroscience witnessed a paradigm shift from functional localization to distributed representations of psychological processes in the brain. Multivariate analyses have been a popular choice to investigate these distributed representations. In the psychological literature, however, the term ``distributeness'' has been used ambiguously and inconsistently, as multivariate representations may be present locally within cortical areas or globally across the entire brain. While local and global multivariate representations are likely encoded at different levels of organisation (across voxels versus across brain areas, respectively), most multivariate analyses are performed without taking the representation's multivariate dimensionality in account. This research proposal aims to investigate the multivariate dimensionality of emotional valence, which is hypothesized to be encoded over brain regions, and contrast this with the locally encoded representations involved in categorical processing. Furthermore, this proposal will exploratively examine how the attribution of valence develops in the brain.}

%%%%%%%%%%%%%%%%%%%% KNITR stuff %%%%%%%%%%%%%%%%%%%%%%%
